Discrete Quantum Theories and Computing

### 2018-12-13 dissertation.tex
dissertation.lyx "Chapter 1 Introduction" Updating...

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

\todo{Type a table for acknowledgment so that I would have to write
``I thank'' so many times here? }Many people in both department
of Mathematics and Computer Science need to do something more to make
my double-major works smoothly. I need to thank all of them, especially
directors of graduate study in Mathematics, especially Prof. Christopher
Judge and Prof. Matthias Weber; directors of Ph.D. study in Computer
Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. Funda
Ergun.

Thank Kin Wai Chan for suggesting me the correct direction for Propsition~\ref{appH.sec},
Prof. 朱樺 for drawing my attention on Prof. Wan's book~\cite{Wan2006},
and Weihua Liu (刘伟华) for remaining me analysts call the right side
of the IVPM outer measure.

@@

Even before quantum mechanics is discovered, human tried to characterize
the physical quantities and manipulate them to simulate and predict
unknown quantities. Discrete quantities can be easily characterized
by whole numbers~\cite{ParkerBaldridge2004}. Even if the proportion
of whole numbers are fractions, the operations among fractions is
essentially the same as those among whole numbers over the common
denominator, and the computational results faithfully represent the
corresponding quantities. In general, discrete computation can be
reliably repeated with exact equivalence, and any digital computer
can faithfully simulate a Turing machine limited only by the available
memory and time~\cite{Turing_1937}.

@@

States Space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %

@@

Local Region\tabularnewline[\doublerulesep]

@@

Likelihood of\tabularnewline[\doublerulesep]

@@

Events is\tabularnewline[\doublerulesep]

@@

Predicted by\tabularnewline[\doublerulesep]

@@

Real-Valued\tabularnewline[\doublerulesep]

@@

Probability\tabularnewline[\doublerulesep]

@@

Impossible\tabularnewline[\doublerulesep]

@@

Probability, but no\tabularnewline[\doublerulesep]

@@

Interval-Valued\tabularnewline[\doublerulesep]

@@

Value\tabularnewline[\doublerulesep]

@@

Yes when Measurement\tabularnewline[\doublerulesep]

@@

Precise Enough\tabularnewline[\doublerulesep]

@@

Transformation\tabularnewline[\doublerulesep]

@@

Included\tabularnewline[\doublerulesep]

@@

Efficiently\tabularnewline[\doublerulesep]

@@

Grover Search\tabularnewline[\doublerulesep]

@@

Algorithm\tabularnewline[\doublerulesep]

>>>>

\usepackage{polyglossia}
\setdefaultlanguage[variant=american]{english}
\setotherlanguage{arabic}
\setotherlanguage{turkish}
\usepackage[style=numeric-comp,sorting=none,maxbibnames=10,doi=false,isbn=false,url=false]{biblatex}
\addbibresource{prop.bib}
\begin{document}
\title{Discrete Quantum Theories and Computing}
\author{Tai, Yu-Tsung}

@@

\todo{Type a table for acknowledgment so that I would have to write
``I thank'' so many times here? }Many people in both department
of Mathematics and Computer Science need to do something more to make
my double-major works smoothly. I need to thank all of them, especially
directors of graduate study in Mathematics, especially Prof. Christopher
Judge and Prof. Matthias Weber; directors of Ph.D. study in Computer
Science, especially Prof. Yuqing Melanie Wu (吴愈青) and Prof. \textturkish{Funda
Ergun}.

Thank Kin Wai Chan for suggesting me the correct direction for Proposition~\ref{appH.sec},
Prof. 朱樺 for drawing my attention on Prof. Wan's book~\cite{Wan2006},
and Weihua Liu (刘伟华) for remaining me analysts call the right side
of the IVPM outer measure.

@@

After first suggesting by Richard Feynman and 40 years theoretical
developments~\cite{Feynman1982Simulating}, IBM, Rigetti, Google,
Microsoft, and many other companies start to build realistic quantum
computers to simulate chemical molecules for drug development and
to improving the classical algorithms like artificial and machine
learning \cite{Shieber2018,Kahn2019}. Before we dive into the issue
between our limitation of distinguishability and quantum theories
and computing, it is instructive to review how classical physical
quantities are characterized and computed.

Discrete quantities can be easily characterized by whole numbers~\cite{ParkerBaldridge2004}.
Even if the proportion of whole numbers are fractions, the operations
among fractions is essentially the same as those among whole numbers
over the common denominator, and the computational results faithfully
represent the corresponding quantities. In general, discrete computation
can be reliably repeated with exact equivalence, and any digital computer
can faithfully simulate a Turing machine limited only by the available
memory and time~\cite{Turing_1937}.

@@

States space & $\mathbb{C}^{D}$ & $\Fq^{D}$ & $\Fpp^{D}$ & %

@@

Local region\tabularnewline[\doublerulesep]

@@

Likelihood\tabularnewline[\doublerulesep]

@@

of events is\tabularnewline[\doublerulesep]

@@

predicted by\tabularnewline[\doublerulesep]

@@

Real-valued\tabularnewline[\doublerulesep]

@@

probability\tabularnewline[\doublerulesep]

@@

impossible\tabularnewline[\doublerulesep]

@@

probability, but no\tabularnewline[\doublerulesep]

@@

Interval-valued\tabularnewline[\doublerulesep]

@@

value\tabularnewline[\doublerulesep]

@@

Yes when measuring\tabularnewline[\doublerulesep]

@@

precise enough\tabularnewline[\doublerulesep]

@@

transformation\tabularnewline[\doublerulesep]

@@

included\tabularnewline[\doublerulesep]

@@

efficiently\tabularnewline[\doublerulesep]

@@

Grover search\tabularnewline[\doublerulesep]

@@

algorithm\tabularnewline[\doublerulesep]
